Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-20 paper.tex
Tuner 1 2

 See \textbf{Figure 1} for an example of a Reducer Network. \note{Desai: Make figure 1}.

\subsection{Tuners}
\note{Desai: can you write this section, I don't know the details}
\subsection{Tuning the Reducer Network}

>>>>

 See \textbf{Figure \ref{fig:red1}} for an example of a Reducer Network. \note{Desai: Make figure 1}.

\begin{figure}[h]
\includegraphics[scale=0.3]{figure/redNetwork.pdf}
\caption{An Reducer Network we used to produce one of our results.
The input shape is sliced into two layers with the stratum partition node.
The top slice is then partitioned into columns. Each column is assigned
a stack of material layers.}
\label{fig:red1}
\end{figure}

\subsection{Tuners}
Tuner is an interface between a Reducer Node and an optimization algorithm.
A Tuner contains a pointer to a Reducer Node and a pointer to a generic optimization subroutine.
When a Tuner is linked to a Reducer Node, 
it can tune the free variables contained in the sub-tree rooted at that node.
\note{Desai: can you write this section, I don't know the details}
\subsection{Tuning the Reducer Network}
A Tuner initializes the optimization by querying the search space from its Reducer Node.
The Reducer Node computes the search space by traversing its sub-tree and collecting
free variables.
The search space specifies the number of free variables, the type of each free variable
(discrete or continuous) and the bounds of these variables.
With the search space specifies, the Tuner's optimization subroutine executes.
The optimization subroutine may ask for additional information such as
the error value of a variable assignment and the gradient. These queries are answered
with call-back functions set up by the Tuner before executing the optimization subroutine.
